\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2012-12-05 paper/mswp2012-proposal.tex
Minimally add some more infos answering the question 'how should the expected results be achieved?'

\subsection{User Centered Design}
\label{subsect:ucd}
We decided on \emph{User Centered Design} as the procedure model used to accompany the creation of the Modern Health Care System because it is a structured method that involves the end users throughout all stages of the design and development of our system. We need to identify and evaluate the users and their needs as a prerequisitory for building an effective and interactive system. User Centered Design is an iterative process that aims at supporting this procedure by integrating the user early into the design process. By the means of user research and a systematic usability enginerring process it is possible to identify how user think and work. User Centered Design focuses on the solution and the quality of the user experience, in contrast to traditional methods that more often emphasize on functionality and robustness of the system. \\

@@

We choose to use Thinking Aloud during the conception of the Modern Health Care System because it helps reveiling \emph{why} users do something. It is very important to integrate Thinking Aloud in a very early stage of the design and development process because early clues can help anticipating and tracing the source of problems and this ultimately leads to a better system and reduced costs.

>>>>

\subsection{User Centered Design}
\label{subsect:ucd}
We decided on \emph{User Centered Design} as the procedure model used to accompany the creation of the Modern Health Care System because it is a structured method that involves the end users throughout all stages of the design and development of our system. We need to identify and evaluate the users and their needs as a prerequisitory for building an effective and interactive system. User Centered Design is an iterative process that aims at supporting this procedure by integrating the user early into the design process. By the means of user research and a systematic usability enginerring process it is possible to identify how user think and work. This enables us to get a better understanding of the actual needs of the users and how to solve their problems by the means of an effective and fun to use system. Moreover we get a better understanding of the motivation and psychological profile of our users, which should help gathering knowledge in the field of gamification.

User Centered Design focuses on the solution and the quality of the user experience, in contrast to traditional methods that more often emphasize on functionality and robustness of the system. \\

@@

We choose to use Thinking Aloud during the conception of the Modern Health Care System because it helps reveiling \emph{why} users do something. It helps us focusing on the interaction needs of the users and to develop a highly integrated ubiquitous system. It is very important to integrate Thinking Aloud in a very early stage of the design and development process because early clues can help anticipating and tracing the source of problems and this ultimately leads to a better system and reduced costs.
